Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2014-05-06 manuscripts/manuscript.Rmd

```{r posterior-mode}
```
```{r stateeq}
```
```{r sdp-pars, dependson="stateeq"}
```
```{r obs, dependson="sdp-pars"}
```

@@

```{r sensitivity, dependson="sensitivity-calc", echo=FALSE, fig.cap="Sensitivity Analysis.  Histogram shows the ratio of the realized net present value / profits derived when managing under the GPDP Gaussian Process approach over the optimal value given the true model and true parameters. Values near 1 indicate nearly optimal performance. Simulations cover a range of underlying parameter, model, replicate, and noise levels."}
ggplot(dat) + geom_histogram(aes(value, fill=noise)) + xlim(0,1.0) + theme_bw() + xlab("value as fraction of the optimal") + facet_wrap(~model, ncol=1)
```

>>>>

```{r posterior-mode}
```
```{r stateeq}
```
```{r sdp-pars, dependson="stateeq"}
```
```{r obs, dependson="sdp-pars", fig.keep='none'}
```

@@

```{r sensitivity, fig.height=6, dependson="sensitivity-calc", echo=FALSE, fig.cap="Sensitivity Analysis.  Histogram shows the ratio of the realized net present value / profits derived when managing under the GPDP Gaussian Process approach over the optimal value given the true model and true parameters. Values near 1 indicate nearly optimal performance. Simulations cover a range of underlying parameter, model, replicate, and noise levels."}
ggplot(dat) + geom_histogram(aes(value, fill=noise)) + xlim(0,1.0) + theme_bw() + xlab("value as fraction of the optimal") + facet_wrap(~model, ncol=1)
```
